Cluster Paper

### 2015-04-24 ms.tex
Added some structural text

\section{Analysis}

@@

We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos, and we find a RMS$[\delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$. \editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight. I don't think that will be the case when we get more complicated things.}

@@

\subsection{Radial Extent}
\begin{equation}
	r_{200} = \bigg{[} \frac{3}{4\pi} \frac{M_{200}}{200\rho_c} \bigg{]}^{1/3}
\end{equation}

\section{Evidence of Substructure}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\subsection{From VD profiles}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\subsection{Mod-Dominance}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\subsection{Dressler-Schectman Test}
We leverage the large spectroscopic dataset to study the structural properties of the clusters. \cite{Pinkney1996} determine, from a comparison of five different methods that the Dressler-Shectman (DS) test \citep{Dressler1988} is the most sensitive to the presence of substructure.

@@

>>>>

\editorial{Should show some sort of a figure which demonstrates the number of recovered galaxies per halo compared to the true number of galaxies in each halo. Maybe even just a statement that the average number of galaxies is XXX and the average number recovered is XXX.}

\section{Recovery of Parameters}

@@

@@

\subsection{Radial Extent}
We define the radius of a galaxy cluster as
\begin{equation}
	r_{200c} = \bigg{[} \frac{3}{4\pi} \frac{M_{200}}{200\rho_c} \bigg{]}^{1/3}
\end{equation}
where $\rho_c$ is critical density of the universe and defined as $3H^2/8\pi G$.

\section{Evidence of Substructure}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsection{From VD profiles}
We utilize the modality \citep{Oliva-Altamirano2014} which describes the Gaussianity of a LOSV distribution in a galaxy cluster. For clusters with Gaussian distributed LOSVs, the modality is close to 1/3. It is defined as $(1+\mathrm{skewness}^2)/(3+\mathrm{kurtosis}^2)$. \editorial{Do I need to describe what the skewness and kurtosis is?}

\subsection{Dominance}
\editorial{This is taken pretty directly from the GAMA paper. Will need to be edited to fit.}
The dominance is defined as the luminosity gap between the brightest and the second brightest galaxy in a cluster ($\Delta m_{1, 2}$). The amplitude of the luminosity gap between the BGG/BCG and the second brightest galaxy in the halo, is expected to be a function of both the formation epoch and the recent infall history of the halo. A small magnitude gap ($\Delta m_{1, 2} < 1$) indicates a recent halo merger, and larger gaps ($\Delta m_{1, 2} > 1$), common in fossil groups, is perhaps indicative of a cluster or groups that has not undergone a recent merger.

\subsection{Dressler-Schectman Test}
We leverage the large spectroscopic dataset to study the structural properties of the clusters. \cite{Pinkney1996} determine, from a comparison of five different methods that the Dressler-Shectman (DS) test \citep{Dressler1988} is the most sensitive to the presence of substructure.

@@

\subsection{Full Knowledge}
We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$. \editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight. I don't think that will be the case when we get more complicated things.}
